Ethnicity Sensitive Author Disambiguation Using Semi-supervised Learning

### 2016-06-27 paper/author_disambiguation.tex
other june 1 fixes
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

\setlength{\intextsep}{5pt plus 0pt minus 0pt}
% \def\baselinestretch{0.99}

\newcommand{\longpage}{\enlargethispage{\baselineskip}}

@@

  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, ``Martinez Torres, A." and ``Torres, A. Martinez").

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig-cuts.pdf}
\caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}
\label{fig:cuts}
\end{figure*}

>>>>

\setlength{\intextsep}{5pt plus 0pt minus 0pt}
%\def\baselinestretch{0.99}

\newcommand{\longpage}{\enlargethispage{1.5\baselineskip}}

@@

  \item An author has multiple surnames (or a patronymic) and some signatures place the first part of the surname within the given names (\eg, ``Martinez Torres, A." and ``Torres, A. Martinez").

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig-cuts.pdf}
\caption{Semi-supervised cut-off strategies to form flat clusters of signatures. Every
dendogram represents a single block.}
\label{fig:cuts}
\end{figure*}
